%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Austin Bennett} \\ \vspace{1pt}
    \small 647-464-7281 $|$ \href{mailto:dev.austinbennett@gmail.com}{dev.austinbennett@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/ausbennett/}{linkedin.com/in/ausbennett} $|$
    \href{https://github.com/ausbennett}{github.com/ausbennett} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {B.Eng. Software Engineering \& Management}{Sept 2019 -- April 2025}
        \begin{itemize}
          \item Notable Coursework: Data Structure \& Algorithms, Software Testing, Databases, Computer Networks \& Security
        \end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Equinix}{Toronto, ON}
      {Software Developer Intern}{May 2024 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Selected as a top 4 finalist in the Equinix Sharktank competition, outshining interns across North America.}
        \resumeItem{Championed the deployment of \textbf{Ansible} as a network configuration management tool, projected to \textbf{save 360 hours annually}.}
        \resumeItem{Automated the conversion of network inventory data to Ansible YAML files using Python and Pandas, streamlining configuration workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {TD Bank}{Toronto, ON}
      {DevOps Engineer Intern}{Jan 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Led cross-team communication for \textbf{Azure Cloud} migration over 3 months, improving scalability and reliability.}
        \resumeItem{Automated release deployments using \textbf{Java Selenium} and \textbf{Rundeck}, saving 2 hours per release cycle.}
        \resumeItem{Managed \textbf{Jenkins CI/CD} processes for \emph{20 builds weekly}, ensuring \emph{85\% successful} build and test rate.}
        \resumeItem{Resolved approximately 10 \textbf{Git} conflicts and \textbf{Jenkins} issues monthly, \emph{reducing resolution time by 25\%}.}
      \resumeItemListEnd

      \resumeSubSubheading
        {Software Engineer Intern}{May 2022 -- Aug 2022}
        \resumeItemListStart
          \resumeItem{Tested \textbf{Spring Boot} REST API for \textbf{Angular} EasyWeb banking applications.}
          \resumeItem{Collaborated closely with the UX/UI design team to transform \textbf{Figma} designs into fully functional and interactive web components.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Finance Platform (Capstone Project)} $|$ \emph{React, Next.js, Express.js, MongoDB}}{Sept 2024 -- April 2025}
          \resumeItemListStart
            \resumeItem{Led the design and development of a financial platform managing \$2M in club funding, enhancing transparency and accountability.}
            \resumeItem{Built the platform from the ground up to support the financial transparency and accountability of student organizations.}
            \resumeItem{Developed a scalable platform using \textbf{React, Next.js, and MongoDB} to streamline club financial processes.}
            \resumeItem{Defined development roadmaps with \textbf{GitHub Projects}, ensuring timely delivery of key features.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Google Student Developer Club $|$ \href{https://github.com/DSC-McMaster-U/ai-journal}{\underline{AI Journal}}, \href{https://github.com/DSC-McMaster-U/Auto-ML}{\underline{AutoML}}}}{Sept 2023 -- April 2025}
          \resumeItemListStart
            \resumeItem{Spearheaded DevOps operations to streamline workflows for both the \textbf{AI Journal Application} \emph{(Espressly)} and \emph{(AutoML)}.}
            \resumeItem{Designed a robust cloud architecture for a user-friendly machine learning service on \textbf{Google Cloud Platform}.}
            \resumeItem{Authored comprehensive \textbf{Docker} configurations for each component of the application stack, enhancing portability and deployment efficiency.}
            \resumeItem{Incorporated \textbf{Terraform} as a core tool in the \textbf{GitHub Actions CI/CD} pipeline, allowing for automated provisioning and management of cloud infrastructure on GCP.}
            \resumeItem{Successfully integrated \textbf{Google Kubernetes Engine} (GKE) to orchestrate container deployment, scaling, and management, achieving high availability and streamlined rollouts of application updates.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------

 \section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Bash, Haskell, HTML, Java, JavaScript, JSON, Python, SQL, TypeScript} \\
     \textbf{Tools \& Platforms}{: Ansible, Atlassian Suite, Azure Cloud, Docker, Figma, GitHub Actions, Google Cloud, Jenkins, Kubernetes, Postman, Selenium, Terraform, VIM} \\
     \textbf{Libraries \& Frameworks}{: Angular, React, Bootstrap, Next.js, Express.js, FastAPI, Flask, Node.js, Spring Boot, NumPy, Pandas, MongoDB, MySQL, JUnit} \\
     \textbf{Credentials}{: Microsoft Azure Fundamentals: AZ-900 (\emph{ID: 7482FE61CE96C076})}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
